Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-23 paper_comparison/paper_comparison/paper_comparison.Rmd
provide more details in x_dist caption

Figure \ref{fig:different-x-dist-poly-power} and Figure \ref{fig:different-x-dist-heter-power} illustrate the change of power of visual tests and conventional tests for different fitted distributions used in the non-linearity model and the heteroskedasticity model. We focus on $log(E) > 2$ where the visual patterns start to become recognisable.

@@

```{r different-x-dist-poly-power, fig.cap = "Comparison of power of conventional tests and visual tests on lineups produced by the non-linearity model under different fitted value distributions."}

>>>>

Figure \ref{fig:different-x-dist-poly-power} illustrates the change of power of visual tests and conventional tests for different fitted distributions used in the non-linearity model and the heteroskedasticity model. We focus on $log(E) > 2$ where the visual patterns start to become recognisable.

@@

```{r different-x-dist-poly-power, fig.cap = "Comparison of power of conventional tests and visual tests on lineups with different fitted value distributions. Each power curve of the uniform distribution is surrounded by a grey line to indicate it is the baseline in its group. Conventional tests are more sensitive than visual tests in regards of the type of the simulated model and the fitted value distribution. For non-linearity patterns, visual tests show lower power with discrete uniform distribution, possibly due to the difficulty in reading discreteness. For heteroskedasticity patterns, because of the unevenness, visual tests have lower power with normal and lognormal distribution."}

### 2023-01-23 paper_comparison/paper_comparison/paper_comparison.tex
provide more details in x_dist caption

Figure \ref{fig:different-x-dist-poly-power} and Figure
\ref{fig:different-x-dist-heter-power} illustrate the change of power of
visual tests and conventional tests for different fitted distributions
used in the non-linearity model and the heteroskedasticity model. We
focus on \(log(E) > 2\) where the visual patterns start to become
recognisable.

@@

\caption{Comparison of power of conventional tests and visual tests on lineups produced by the non-linearity model under different fitted value distributions.}\label{fig:different-x-dist-poly-power}
\end{figure}

>>>>

Figure \ref{fig:different-x-dist-poly-power} illustrates the change of
power of visual tests and conventional tests for different fitted
distributions used in the non-linearity model and the heteroskedasticity
model. We focus on \(log(E) > 2\) where the visual patterns start to
become recognisable.

@@

\caption{Comparison of power of conventional tests and visual tests on lineups with different fitted value distributions. Each power curve of the uniform distribution is surrounded by a grey line to indicate it is the baseline in its group. Conventional tests are more sensitive than visual tests in regards of the type of the simulated model and the fitted value distribution. For non-linearity patterns, visual tests show lower power with discrete uniform distribution, possibly due to the difficulty in reading discreteness. For heteroskedasticity patterns, because of the unevenness, visual tests have lower power with normal and lognormal distribution.}\label{fig:different-x-dist-poly-power}
\end{figure}
